---
title: "nlgeocoder"
author: "Edwin de Jonge, Egge-Jan Pollé, Willy Tadema, "
date: "9/11/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(leaflet)
library(sf)
```

## Geocoding for nl

Who are we:

- Egge-Jan Pollé (NL)
- Willy Tadema (NL)
- Edwin de Jonge (NL)
- Juris Breidaks (LV)

## What is it about?

### PDOK: dutch webservice

- Providing **location service**s as a Web API:
  - e.g. finding address -> location coordinates
  - deduplicating addressess ("town road" vs "town street" vs "town alley")
- Providing geo **tile layer**s.
  - style: "gray", "brt", "", ""

### Why?

- Location services of Google / Openstreetmap don't suffice


## 

```{r, echo = TRUE, eval=TRUE}
library(nlgeocoder)
library(leaflet)
r <- nl_geocode("Henri Faasdreef")
leaflet() %>% addPdokTiles("gray") %>% addMarkers(data = r)
```

##
```{r, echo = FALSE, eval=TRUE}
library(nlgeocoder)
library(leaflet)
r <- nl_geocode("Henri Faasdreef")
leaflet() %>% addPdokTiles("gray") %>% addMarkers(data = r)
```
