---
title: "nlgeocoder"
subtitle: "Geocoder for NL"
author: ''
date: "September 14 2018"
output:
  ioslides_presentation: default
  revealjs::revealjs_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(leaflet)
library(sf)
```

## Geocoding for nl

### We are:

- Egge-Jan Pollé (NL)
- Willy Tadema (NL)
- Edwin de Jonge (NL)
- Juris Breidaks (LV)


## What is it about?

### PDOK: dutch webservice

- Providing **location service**s as a Web API:
  - Search: "address",return: coordinates, regional administrative info (>30).
  - deduplicating addresses ("town road" vs "town street" vs "town alley")
- Providing geo **tile layer**s.
  - restricts topographic details to NL. 
  - style: "gray", "brt", "aerial" and "pastel"

## `nl_geocode`

## `nl_free`, `nl_suggest`, `nl_lookup`

## `addPdokTiles`


## Example

```{r, echo = TRUE, eval=TRUE}
library(nlgeocoder)
library(leaflet)
r <- nl_geocode("Henri Faasdreef 312") # uRos 2018 Conference!
leaflet() %>% addPdokTiles("gray") %>% 
  addMarkers(data = r, popup = ~weergavenaam)
```
